\title{Performance Figures}
\def \documentid {FLIGHTOS-UVIE-PERF-001}
\date{Draf 0.1, January 19, 2021}

\newcommand\affil[1]{\textsuperscript#1}

\def\preparedby {Armin Luntzer\affil{1}}
\def\checkedby {Roland Ottensamer\affil{1}}
\def\approvedby {Franz Kerschbaum\affil{1}}

\def\affiliations{
	\affil{1} Department of Astrophysics, University of Vienna
}




\input{../shared/template/univie.tex}
\input{../shared/template/titlepage.tex}
%\input{../shared/glossary.tex}


\usepackage{vhistory}

\usepackage[giveninits=true]{biblatex}
\addbibresource{../shared/bibliography.bib}

\usepackage{listings}

\lstdefinestyle{customc}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  xleftmargin=\parindent,
  language=C,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{uvie-orangered!75},
  commentstyle=\itshape\color{uvie-gray},
  identifierstyle=\color{uvie-blue},
  stringstyle=\color{uvie-goldenyellow},
}

\usepackage{appendix}

\begin{document}
\lstset{style=customc} 


\setmainfont{MyriadPro-SemiCondensed}
\uvietitlepage%
{UVIE FlightOS}%
{\doctitle}%
{../shared/images/logo2.pdf}
\setmainfont{MyriadPro}

\approvalpage

\tableofcontents
\newpage



\begin{versionhistory}
  \vhEntry{0.1}{19.01.2021}{AL}{Initial version}
\end{versionhistory}


\chapter{Introduction}

\section{Purpose of the Document}

This document is a collection of various performance figures of the FlightOS
operating system on target platforms such as the GR712 or GR740.

\chapter{Applicable and Reference Documents} % does not break automatically for some reason

\printbibliography[heading=none]


\chapter{Terms, Definitions and Abbreviated Items}
%\printglossary[type=acronym]
%\printglossary[type=main, style=altlist]


\chapter{Timing System}\label{chap:timing}

\section{Overview}

The internal timekeeping system in FlightOS relies upon a hardware
clock device which returns the current system uptime in seconds and nanoseconds.
This clock device is implemented in the architecture specific section with
an interface compatible to \emph{struct clocksource} and registered to
the main kernel \emph{ktime} interface by the architecture specific
bootup sequence.

Upon registration of the clocksource, the ktime subsystem calibrates the
uptime clock readout overhead by reading the uptime clock for a configurable
number of repetitions. For each readout, the $\Delta t$ to the previous
update is calculated and accumulated. The accumulated $\Delta t$ is the
averaged over the number of loops and divided by 2 to account for the
period between two successive readouts. This value is then stored and
added to all timesamps retrieved by calls to \emph{ktime\_get()} as a
correcting offset.

Another timing-related kernel subsystem are \emph{clockevent} devices,
which are registered by the architecture specific bootup code. These devices
can have properties such as periodic and on-shot timeouts, or absolute timings
given a particular ktime.

Available clockevent devices are offered to the \emph{tick} subsystem by the 
architecture code for each booting SMP CPU to support thread scheduling. The
tick system checks the device properties and may also exchange an already
registered clockevent device for one with better characteristics. When a
clockevent device is registered, its minimum processable tick length
is calibrated and also serves as a benchmark of interrupt jitter.



\section{Performance Figures: GR712}

In the GR712, the \emph{General Purpose Timer Unit with Time Latch Capability}\cite{GR712UM}
is used as the architecture-specific uptime clock. The prescaler for this timer
is set to 4 by default. One of the timers is configured to underflow once
per second. The needed value depends on the CPU clock frequency and therefore
the calculated baseline precision of the clock is \emph{ (4 + 1) / freq)} or 500 ns 
for a system clock of 10 MHz.


The measured precision is however lower, as it is increased by the
instruction in the code path to read out the uptime clock.

For the \emph{GR712RC Dual-Core LEON3-FT Development Board} at a clock speed of
80 MHz, the total readout overhead amounts to < 850 ns.

For the \emph{GR712 CHEOPS DPU prototype board} clocked at 25 MHz
the overhead is < 2700 ns.



\chapter{Interrupt Timings}

\section{Overview}

Interrupts and interrupt handling timings as well as their jitter depend on a
multitude of factors such as concurrent number of raised interrupts, memory bus
loads, states of instruction and data caches and so on. This chapter is only
concerned with the software related effects.

The \emph{tick} subsystem of the kernel can be used to establish a baseline
of interrupt jitter and predictability, as the clockevent devices (\ref{chap:timing})
are calibrated at bootup. This is done by registering a special tick calibration
hander to the ISR-driven callback of the clockevent device. The clockevent
timeout is then programmed to the calibrated kernel uptime clock readout overhead
and the minimum tick period of the device is monitored for each pass of a loop,
which increased the clockevent timeout by the uptime clock overhead until the
minimum tick period parameter for the device is set by the calibration callback
handler. This is done because a clockevent device is required to
cause a timer IRQ to be raised every time a timeout is programmed, regardless
of the underlying precision of the clock. That means that even a timeout of 0
must result in an (immediate) interrupt).

When a value for the minimum tick period is established, a calibration loop
is executed to establish an average minimum period by repeating the
above process multiple time for the found timeout period. The average
minimum tick timeout is then doubled for extra margin and set in the
configuration paramters of the clockevent device.

The values for the minimum tick period represent the lower limit of the
achievable scheduling event cadence for the given system configuration.


\section{Performance Figures: GR712}

On the GR712, the \emph{General Purpose Timer Unit}\cite{GR712UM} is used for
the architecture-specific clockevent devices. The prescaler for these timers
is set to 7 by default. The timer precision also depends on the CPU clock
frequency and therefore the calculated baseline precision of these clockevent
devices is \emph{ (7 + 1) / freq)} or 800 ns for a system clock of 10 MHz.

The measured minimum timeout is however much higher, as it is defined by the
instructions executed in the code path of the clockdevice implmentation and the
setup of the interrupt context in the CPU.

For the \emph{GR712RC Dual-Core LEON3-FT Development Board} at a clock speed of
80 MHz, the timer units calibrate to $10 \pm 0.2$ µs and $12 \pm 0.5$ µs for
CPUs 0 and 1 respectively.

The same test was run on the \emph{GR712 CHEOPS DPU prototype board} clocked
at 25 MHz and resulted in $30\pm 0.3$ µs and $32 \pm 0.3$ µs.

Note that the above values are doubled in the software for extra safety margin.





\end{document}
