

\title{Test Specification}
\def \documentid {LEANOS-UVIE-TS-001}
\date{Issue 0.2, May 2, 2016}

\newcommand\affil[1]{\textsuperscript#1}

\def\preparedby {Armin Luntzer\affil{1}}
\def\checkedby {Roland Ottensamer\affil{1}}
\def\approvedby {Franz Kerschbaum\affil{1}}

\def\affiliations{
	\affil{1} Department of Astrophysics, University of Vienna
}

\input{../shared/template/univie.tex}
\input{../shared/template/titlepage.tex}
\input{../shared/template/traceability.tex}
\input{../shared/glossary.tex}

\usepackage{vhistory}

\usepackage{biblatex}
\addbibresource{../shared/bibliography.bib}


\externaldocument[REQ-]{../testplan/testplan}
\input{../testplan/requirements.list}


\rereadauxdesignlabels


\begin{document}


\setmainfont{MyriadPro-SemiCondensed}
\uvietitlepage%
{Lean OS --\\ An operating system for the SSDP}%
{\doctitle}%
{../shared/images/logo2.pdf}
\setmainfont{MyriadPro}

\approvalpage

\tableofcontents
\newpage


\chapter*{List of Specified Tests}
\label{listoftests}
\the\designlist


\begin{versionhistory}
  \vhEntry{0.1}{01.05.2017}{AL}{Initial version}
\end{versionhistory}


\chapter{Introduction}


\section{Purpose of the Document}

The test plan for the the LeanOS operating system is defined in
\cite{leanosTP}.\\
\\

\noindent
This test plan includes acceptance tests where the integrated operating
system is subjected to tests in its operational environment.\\

\noindent
This document specifies the acceptance tests for LeanOS.\\

\noindent
A test is specified by defining the:
\begin{itemize}
	\item pre-conditions for the test
	\item hardware baseline
	\item system configuration
	\item checks to be performed
	\item pass/fail criterea
\end{itemize}



\section{Test Overview}

A list of tests specified in this document is available in chapter:
\nameref{listoftests}


\chapter{Applicable and Reference Documents} % does not break automatically for some reason

\printbibliography[heading=none]


\chapter{Terms, Definitions and Abbreviated Items}

\printglossary[type=acronym]
\printglossary[type=main, style=altlist]


\chapter{Test Specification}

\section{Unit and Integration Tests}

\design{UIT-0001}
{Test Implementation}{%
For each software component or module, a corresponding unit or integration test
program is implemented by means of an adapted version of the \emph{kselftest}
framework. A shared collection of mockup and stub functions is maintained in
order to facilitate testing.
}%
{\meetsreq{UIT-0001, UITE-0001}}{}

{Test Coverage}{%
All implemented unit tests deliver 100\% statement, decision and condition
coverage. Any deviations are justified as part of the unit test implementation.
}%
{\meetsreq{SCC-0004}}{}

\design{UIT-0002}
{Test Suite}{%
All unit and integration tests, along with stub and mockup functions are stored
in the LeanOS source tree directory \mbox{\emph{tools/testing/unittest/}}.
}%
{\meetsreq{UIT-0002, UITE-0001}}{}

\design{UIT-0003}
{Test Exection}{%
The collection of unit and integration tests is executable from the specified
source directory via the \emph{make} command.
}%
{\meetsreq{UIT-0003}}{}


\design{UIT-0004}
{Test Results}{%
The test executables generate human readable text output summarising the number,
types and outcome of each test performed.
}%
{\meetsreq{UIT-0004}}{}


\design{UIT-0005}
{Automated Testing}{%
The test executables report failed tests as shell exit codes, so the outcome
can be detected by an external test program such as \emph{git bisect}.
}%
{\meetsreq{UIT-0005}}{}




\section{Hardware-Software Tests}

\design{HST-0001}
{Test Implementation}{%
For each software component or module that neeeds verification in a hardware
environment, a test program is implemented.
}%
{\meetsreq{HST-0001}}{Since these tests typically involve more complex control %
via other tools (such as \emph{grmon} or \gls{SpaceWire} interfaces), they are %
implemented as shell scripts that set up the required configuration and %
executes the test on the target hardware. %
}


\design{HST-0002}
{Test Suite}{%
All hardware-software tests are stored in the LeanOS source
tree directory \mbox{\emph{tools/testing/hwtests/}}.%
}%
{\meetsreq{HST-0002}}{}


\design{HST-0003}
{Test Results}{%
The test executables generate human readable text output summarising the number,
types and outcome of each test performed.
}%
{\meetsreq{HST-0003}}{}


\design{HST-0004}
{Automated Testing}{%
The test executables report failed tests as shell exit codes, so the outcome
can be detected by an external test program such as \emph{git bisect}.
}%
{\meetsreq{HST-0004}}{}


\design{SCC-0001}
{Code Coverage}{%
Statement, decision and condition coverage is determined via \emph{gcov}.
A \emph{make} target \emph{coverage\_test} is available in the \emph{Makefile}
of the unit test directory of the LeanOS source tree.
Human-readable reports are placed in the respective subdirectories for each
individual unit test.
}%
{\meetsreq{SCC-0001, SCC-0002, SCC-0003}}{}



\chapter{Test Plan Requirements to Specification Traceability}

\noindent
Functional requirements are always reference to their specifications, others
only as needed or for clarification. This is reflected in the traceability
matrix.

\traceabilitymatrix

\end{document}
